---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Eric Kirkendall"
date: "8/29/2019"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

(There are 1843 rows and 3 columns in datasauRus_dozen. There are 3 vairables that are: dataset, x, and y)

### Exercise 2

(The answers for this Exercise are given for you below. But you should clean up some of the narrative so that it only includes what you want to turn in.)

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Plotting dataset "star"

```{r plot-star}
star_data <- datasaurus_dozen %>%
+     filter(dataset == "star")
 
 ggplot(data = star_data, mapping = aes(x = x, y = y)) +
+     geom_point()
```

Calculating R for Dataset "star"

```{r cor-star}
  star_data %>%
+ summarize(r = cor(x,y))
```

### Exercise 4

Plotting dataset "cirlce"

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  + filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  + geom_point()
```

Calculating R for dataset "circle

```{r cor-circle}
circle_data %>%
+ summarize(r = cor(x,y))
```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)