---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Eric Kirkendall"
date: "8/29/2019"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

(There are 1843 rows and 3 columns in datasauRus_dozen. There are 3 vairables that are: dataset, x, and y)

### Exercise 2

Plotting Dino Dataset

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calcuylating R for Dataset Dino

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
R = -0.0645
### Exercise 3

Plotting dataset "star"

```{r plot-star}
star_data <- datasaurus_dozen %>%
+     filter(dataset == "star")
 
 ggplot(data = star_data, mapping = aes(x = x, y = y)) +
+     geom_point()
```

Calculating R for Dataset "star"

```{r cor-star}
  star_data %>%
+ summarize(r = cor(x,y))
```
R = -0.0630
R values are very similar but this r value is slightly weaker than that of Dino.
### Exercise 4

Plotting dataset "cirlce"

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  + filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  + geom_point()
```

Calculating R for dataset "circle

```{r cor-circle}
circle_data %>%
+ summarize(r = cor(x,y))
```
R = -0.0683
This R value is still small but slightly stronger than those of Dino and Star.
### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)